### 2022-02-18 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@4521b6e6879c8d9b86f4b4ba38f826f373b680b7 🚀

In fig.~\ref{fig:concept}, we provide a methodological overview based on
learning the embedding of a metaweb of trophic interactions for European
mammals (known interactions; Maiorano et al., 2020a, 2020b) and, based
on phylogenetic relationships between mammals globally (\emph{i.e.},
phylogenetic tree Upham et al., 2019), infer a metaweb for the Canadian
mammalian species pool (using only a species list \emph{i.e.}
interactions are treated as unknown in this instance). Our case study
shows that phylogenetic transfer learning is an effective approach to
the generation of probabilistic metawebs. This showcases that although
the components (species) that make up the Canadian and European
communities may be \emph{minimally} shared (the overall species overlap
is less than 4\%), if the medium (proxy space) selected in the transfer
step is biologically plausible, we can still effectively learn from the
known network and make biologically relevant predictions of
interactions. Indeed, as we detail in the results, when validated
against the known (but fractional) data of trophic interactions present
between Canadian mammals, our model achieves a predictive accuracy of
approximately 91\%.

@@

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple; left-side
matrix) and right (green/brown; top matrix) subspaces, alongside the
adjacency matrix of the food web they encode (greyscale). The European
metaweb is on the left, and the imputed Canadian metaweb (before data
inflation) on the right. This figure illustrates how much structure the
left subspace captures. As we show in fig.~\ref{fig:degree}, the species
with a value of 0 in the left subspace are species without any
prey.}\label{fig:subspaces}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:inflation}{%
\centering
\includegraphics{figures/figure-validation.png}
\caption{Left: comparison of the probabilities of interactions assigned
by the model to all interactions (grey curve), the subset of
interactions found in GloBI (red), and in the Strong \& Leroux (2014)
Newfoundland dataset (blue). The model recovers more interactions with a
low probability compared to data mining, which can suggest that
collected datasets are biased towards more common or easy to identify
interactions. Right: distribution of the in-degree and out-degree of the
mammals from Canada in the reconstructed metaweb. This figure describes
a flat, relatively short food web, in which there are few predators but
a large number of preys.}\label{fig:inflation}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:degree}{%
\centering
\includegraphics{figures/figure-degree.png}
\caption{Top: biological significance of the first dimension. Left:
there is a linear relationship between the values on the first dimension
of the left subspace and the generality, \emph{i.e.} the relative number
of preys, \emph{sensu} Schoener (1989). Species with a value of 0 in
this subspace are at the bottom-most trophic level. Right: there is,
similarly, a linear relationship between the position of a species on
the first dimension of the right subspace and its vulnerability,
\emph{i.e.} the relative number of predators. Taken together, these two
figures show that the first-order representation of this network would
capture its degree distribution. Bottom: topological consequences of the
first dimension. Left: differences in the \(z\)-scores of the actual
configuration model for the reconstructed network, and the prediction
based only on the first dimension. Right: distribution of the
differences in the left panel.}\label{fig:degree}
}
\end{figure}

>>>>

In fig.~\ref{fig:concept}, we provide a methodological overview based on
learning the embedding of a metaweb of trophic interactions for European
mammals (known interactions; Maiorano et al., 2020a, 2020b) and, based
on phylogenetic relationships between mammals globally (\emph{i.e.},
phylogenetic tree Upham et al., 2019), infer a metaweb for the Canadian
mammalian species pool (using only a species list \emph{i.e.} we have no
prior data on species interaction data for Canada in this instance). Our
case study shows that phylogenetic transfer learning is an effective
approach to the generation of probabilistic metawebs. This showcases
that although the components (species) that make up the Canadian and
European communities may be \emph{minimally} shared (the overall species
overlap is less than 4\%), if the medium (proxy space) selected in the
transfer step is biologically plausible, we can still effectively learn
from the known network and make biologically relevant predictions of
interactions. Indeed, as we detail in the results, when validated
against the known (but fractional) data of trophic interactions present
between Canadian mammals, our model achieves a predictive accuracy of
approximately 91\%.

@@

\begin{figure}
\hypertarget{fig:subspaces}{%
\centering
\includegraphics{figures/figure-subspaces.png}
\caption{Visual representation of the left (green/purple; left-side
matrix) and right (green/brown; top matrix) subspaces, alongside the
adjacency matrix of the food web they encode (greyscale). Where the
color saturation is the magnitude of the latent trait value. The
European metaweb is on the left, and the imputed Canadian metaweb
(before data inflation) on the right. This figure illustrates how much
structure the left subspace captures. As we show in
fig.~\ref{fig:degree}, the species with a value of 0 in the left
subspace are species without any prey.}\label{fig:subspaces}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:inflation}{%
\centering
\includegraphics{figures/figure-validation.png}
\caption{Left: comparison of the probabilities of interactions assigned
by the model to all interactions (grey curve), the subset of
interactions found in GloBI (red), and in the Strong \& Leroux (2014)
Newfoundland dataset (blue). The model recovers more interactions with a
low probability compared to data mining, which can suggest that
collected datasets are biased towards more common or easy to identify
interactions. Right: distribution of the in-degree and out-degree of the
mammals from Canada in the reconstructed metaweb, where the rank is the
maximal number of linearly independent columns (interactions) in the
metaweb. This figure describes a flat, relatively short food web, in
which there are few predators but a large number of
preys.}\label{fig:inflation}
}
\end{figure}

@@

\begin{figure}
\hypertarget{fig:degree}{%
\centering
\includegraphics{figures/figure-degree.png}
\caption{Top: biological significance of the first dimension. Left:
there is a linear relationship between the values on the first dimension
of the left subspace and the generality, \emph{i.e.} the relative number
of preys, \emph{sensu} Schoener (1989). Species with a value of 0 in
this subspace are at the bottom-most trophic level. Right: there is,
similarly, a linear relationship between the position of a species on
the first dimension of the right subspace and its vulnerability,
\emph{i.e.} the relative number of predators. Taken together, these two
figures show that the first-order representation of this network would
capture its degree distribution. Bottom: topological consequences of the
first dimension. Left: differences in the \(z\)-scores of the actual
configuration model for the reconstructed network and the prediction
based only on the first dimension (with a deeper saturation indicating a
bigger difference in scores). Right: distribution of the differences in
the left panel.}\label{fig:degree}
}
\end{figure}
